Embryo provides a minimal set of native calls that can be used within any Embryo script.

Those calls are detailed here.

\begin{Desc}
\item[Note:]Some of the \char`\"{}core\char`\"{} functions here are also described in the full Small documentation given\end{Desc}
\begin{Desc}
\item[\hyperlink{todo__todo000003}{Todo}]Finish this section.\end{Desc}
\hypertarget{Available_Native_Calls_Page_Args_ANC_Section}{}\section{Argument Functions}\label{Available_Native_Calls_Page_Args_ANC_Section}
\hypertarget{Available_Native_Calls_Page_Numargs_Desc}{}\subsection{numargs}\label{Available_Native_Calls_Page_Numargs_Desc}
Returns the number of arguments passed to a function. Useful when dealing with variable argument lists.\hypertarget{Available_Native_Calls_Page_Getargs_Desc}{}\subsection{getarg(arg, index=0)}\label{Available_Native_Calls_Page_Getargs_Desc}
Retrieves the argument number {\tt arg}. If the argument is an array, use {\tt index} to specify the index of the array to return.\hypertarget{Available_Native_Calls_Page_Setargs_Desc}{}\subsection{setargs(arg, index=0, value)}\label{Available_Native_Calls_Page_Setargs_Desc}
Sets the argument number {\tt arg} to the given {\tt arg}. {\tt index} specifies the index of {\tt arg} to set if {\tt arg} is an array.\hypertarget{Available_Native_Calls_Page_String_ANC_Section}{}\section{String Functions}\label{Available_Native_Calls_Page_String_ANC_Section}
Functions that work on strings.\hypertarget{Available_Native_Calls_Page_Atoi_Desc}{}\subsection{atoi}\label{Available_Native_Calls_Page_Atoi_Desc}
Translates an number in string form into an integer.\hypertarget{Available_Native_Calls_Page_Fnmatch_Desc}{}\subsection{fnmatch}\label{Available_Native_Calls_Page_Fnmatch_Desc}
Buggered if I know what this does?\hypertarget{Available_Native_Calls_Page_Strcmp_Desc}{}\subsection{strcmp}\label{Available_Native_Calls_Page_Strcmp_Desc}
String comparing function.\hypertarget{Available_Native_Calls_Page_Float_ANC_Section}{}\section{Float Functions}\label{Available_Native_Calls_Page_Float_ANC_Section}
\hypertarget{Available_Native_Calls_Page_Float_Desc}{}\subsection{float}\label{Available_Native_Calls_Page_Float_Desc}
\hypertarget{Available_Native_Calls_Page_Atof_Desc}{}\subsection{atof}\label{Available_Native_Calls_Page_Atof_Desc}
\hypertarget{Available_Native_Calls_Page_Float_Mul_Desc}{}\subsection{float\_\-mul}\label{Available_Native_Calls_Page_Float_Mul_Desc}
\hypertarget{Available_Native_Calls_Page_Float_Div_Desc}{}\subsection{float\_\-div}\label{Available_Native_Calls_Page_Float_Div_Desc}
\hypertarget{Available_Native_Calls_Page_Float_Add_Desc}{}\subsection{float\_\-add}\label{Available_Native_Calls_Page_Float_Add_Desc}
\hypertarget{Available_Native_Calls_Page_Float_Sub_Desc}{}\subsection{float\_\-sub}\label{Available_Native_Calls_Page_Float_Sub_Desc}
\hypertarget{Available_Native_Calls_Page_Fract_Desc}{}\subsection{fract}\label{Available_Native_Calls_Page_Fract_Desc}
\hypertarget{Available_Native_Calls_Page_Round_Desc}{}\subsection{round}\label{Available_Native_Calls_Page_Round_Desc}
\hypertarget{Available_Native_Calls_Page_Float_Cmp_Desc}{}\subsection{float\_\-cmp}\label{Available_Native_Calls_Page_Float_Cmp_Desc}
\hypertarget{Available_Native_Calls_Page_Sqrt_Desc}{}\subsection{sqrt}\label{Available_Native_Calls_Page_Sqrt_Desc}
\hypertarget{Available_Native_Calls_Page_Pow_Desc}{}\subsection{pow}\label{Available_Native_Calls_Page_Pow_Desc}
\hypertarget{Available_Native_Calls_Page_Log_Desc}{}\subsection{log}\label{Available_Native_Calls_Page_Log_Desc}
\hypertarget{Available_Native_Calls_Page_Sin_Desc}{}\subsection{sin}\label{Available_Native_Calls_Page_Sin_Desc}
\hypertarget{Available_Native_Calls_Page_Cos_Desc}{}\subsection{cos}\label{Available_Native_Calls_Page_Cos_Desc}
\hypertarget{Available_Native_Calls_Page_Tan_Desc}{}\subsection{tan}\label{Available_Native_Calls_Page_Tan_Desc}
\hypertarget{Available_Native_Calls_Page_Abs_Desc}{}\subsection{abs}\label{Available_Native_Calls_Page_Abs_Desc}
Returns the absolute value of the given float.\hypertarget{Available_Native_Calls_Page_Time_ANC_Section}{}\section{Time Functions}\label{Available_Native_Calls_Page_Time_ANC_Section}
\hypertarget{Available_Native_Calls_Page_Seconds_Desc}{}\subsection{seconds()}\label{Available_Native_Calls_Page_Seconds_Desc}
\hypertarget{Available_Native_Calls_Page_Date_Desc}{}\subsection{date}\label{Available_Native_Calls_Page_Date_Desc}
\hypertarget{Available_Native_Calls_Page_Rand_ANC_Section}{}\section{Random Functions}\label{Available_Native_Calls_Page_Rand_ANC_Section}
\hypertarget{Available_Native_Calls_Page_Rand_Desc}{}\subsection{rand()}\label{Available_Native_Calls_Page_Rand_Desc}
Returns a random integer.\hypertarget{Available_Native_Calls_Page_Randf_Desc}{}\subsection{randf()}\label{Available_Native_Calls_Page_Randf_Desc}
Returns a random float. 